Distanced-based VOCC analysis

### 2020-02-06 analysis/VOCC/bioclimatic/4-vocc-bioclimatic.Rmd
organize old code

---
title: "BACI of `r paste(params$species)` biomass for `r paste(params$region)` VOCC"
author: "Philina English"
date: "`r Sys.Date()`"
output: html_document 
params: 
    species: "Pacific Cod" 
    #region: "both odd year surveys"
    region: "West Coast Vancouver Island"
    age: "mature"
    biomass_threshold: "50"
    climate: "temperature"
    threshold: 0.5
editor_options: 
  chunk_output_type: inline
---

@@

    if (climate == "temperature") {
      vocc$diff <- vocc$units_per_decade / 10 * delta_t_total
      vocc_plot <- plot_vocc(vocc,  
        theme_black = TRUE,
        coast = TRUE,
        vec_aes = "distance",
        vec_col = "white",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "temp_e",
        fill_label = paste(" Temperature\n change\n", 
          start_time, "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        raster_limits = c(raster_min, raster_max),
        na_colour = "gray",
        # white_zero = TRUE,
        vec_alpha = 0.35,
        axis_lables = FALSE,
        transform_col = no_trans
      ) + ggtitle(climate)
    }

    if (climate == "do") {
      vocc$diff <- vocc$units_per_decade / 10 * delta_t_total
      vocc_plot <- plot_vocc(vocc, 
        theme_black = TRUE,
        coast = TRUE,
        vec_aes = "distance",
        vec_col = "white",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "do_est_e",
        fill_label = paste(" DO change\n", start_time, 
          "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        raster_limits = c(raster_min, raster_max),
        na_colour = "gray",
        # white_zero = TRUE,
        # high_fill = "Steel Blue 4",
        # low_fill = "Red 3",
        vec_alpha = 0.35,
        axis_lables = FALSE,
        transform_col = no_trans
      ) + ggtitle(climate)
    }

@@

      vocc_plot_temp <- plot_vocc(vocc, 
        vec_aes = "distance",
        vec_col = "white",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "temp_e",
        fill_label = paste(" Temperature\n change\n", 
          start_time, "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        #raster_limits = c(raster_min_temp, raster_max_temp),
        # white_zero = TRUE,
        vec_alpha = 0.35,
        axis_lables = FALSE,
        transform_col = no_trans
      ) + ggtitle("temperature")

@@

    if (climate == "temperature") {
      vocc$diff <- vocc$units_per_decade / 10 * delta_t_total
      vocc_plot <- plot_vocc(vocc, 
        theme_black = TRUE,
        coast = TRUE,
        vec_aes = "distance",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "diff",
        fill_label = paste(" Temperature\n change\n", start_time, "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        #raster_limits = c(raster_min, raster_max),
        na_colour = "#9E0142",
        # mid_fill = NULL, #"#FFFEC9", #cream
        # high_fill = "#D53E4F",#"Steel Blue 4"
        # low_fill = "#5E4FA2",
        white_zero = TRUE,
        vec_col = "white",
        vec_alpha = 0.45,
        axis_lables = FALSE,
        transform_col =  sqrt #fourth_root_power
      ) + ggtitle(climate) #+ ggpubr::theme_transparent()# +  theme_black()
    }

    if (climate == "do") {
      vocc$diff <- vocc$units_per_decade / 10 * delta_t_total
      vocc_plot <- plot_vocc(vocc,  
        theme_black = TRUE,
        coast = TRUE,
        vec_aes = "distance",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "diff",
        fill_label = paste(" DO change\n", start_time, "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        #raster_limits = c(raster_min, raster_max),
        na_colour = "gray",
        white_zero = TRUE,
        high_fill = "Steel Blue 4",
        low_fill = "Red 3",
        vec_alpha = 0.65,
        axis_lables = FALSE,
        transform_col = sqrt# no_trans
      ) + ggtitle(climate)
    }

@@

      vocc_plot_temp <- plot_vocc(vocc,  
        theme_black = TRUE,
        coast = TRUE,
        vec_aes = "distance",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "temp_diff",
        fill_label = paste(" Temperature\n change\n", start_time, "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        raster_limits = c(raster_min_temp, raster_max_temp),
        white_zero = TRUE,
      vec_alpha = 0.65,
        axis_lables = FALSE,
        transform_col = sqrt #no_trans
      ) + ggtitle("temperature")

@@

      vocc_plot_do <- plot_vocc(vocc,  
        theme_black = TRUE,
        coast = TRUE,
        vec_aes = "distance",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "do_diff",
        fill_label = paste(" DO change\n", start_time, "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        raster_limits = c(raster_min_do, raster_max_do),
        white_zero = TRUE,
        high_fill = "Steel Blue 3",
        low_fill = "Red 2",
      vec_alpha = 0.65,
        axis_lables = FALSE,
        transform_col = sqrt #no_trans
      ) + ggtitle("do")

@@

      vocc_plot <- plot_vocc(vectors,
        theme_black = TRUE,
        coast = TRUE,
        vec_aes = "distance",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "diff",
        fill_label = paste("Temperature\n change\n", start_time, "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        raster_limits = c(raster_min, raster_max),
        na_colour = "gray",
        white_zero = TRUE,
      vec_alpha = 0.65,
        axis_lables = FALSE,
        transform_col = no_trans
      ) + ggtitle(paste0(threshold, " units of ", climate, " change below ", 
        biomass_threshold, "% of peak predicted ", species, " biomass" ))
    }

@@

      vocc_plot <- plot_vocc(vectors,
        theme_black = TRUE,
        coast = TRUE,
        vec_aes = "distance",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "diff",
        fill_label = paste("DO change\n", start_time, "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        raster_limits = c(raster_min, raster_max),
        na_colour = "gray",
        white_zero = TRUE,
        high_fill = "Steel Blue 4",
        low_fill = "Red 3",
        vec_alpha = 0.65,
        axis_lables = FALSE,
        transform_col = no_trans
      ) + ggtitle(paste0(threshold, " units of ", climate, " change below ", 
        biomass_threshold, "% of peak predicted ", species, " biomass" ))
    }

@@

      vocc_plot_temp <- plot_vocc(vectors,
        theme_black = TRUE,
        coast = TRUE,
        vec_aes = "distance",
        min_vec_plotted = input_cell_size,
        NA_label = ".",
        fill_col = "temp_diff",
        fill_label = paste(
          "Change from\n",
          start_time, "to", start_time + delta_t_total, ""
        ),
        raster_alpha = 1,
        raster_limits = c(raster_min_temp, raster_max_temp),
        na_colour = "gray",
        white_zero = TRUE,
        vec_alpha = 0.65,
        axis_lables = FALSE,
        transform_col = no_trans
      ) + ggtitle("temperature")

@@

      vocc_plot_do <- plot_vocc(vectors,
        theme_black = TRUE,
        coast = TRUE,
        vec_aes = "distance",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "do_diff",
        fill_label = paste(
          "Change from\n",
          start_time, "to", start_time + delta_t_total, ""
        ),
        raster_alpha = 1,
        raster_limits = c(raster_min_do, raster_max_do),
        na_colour = "gray",
        white_zero = TRUE,
        high_fill = "Steel Blue 4",
        low_fill = "Red 3",
        vec_alpha = 0.65,
        axis_lables = FALSE,
        transform_col = no_trans
      ) + ggtitle("do")

@@

    vocc_plot <- plot_vocc(biomass,
        theme_black = TRUE,
        coast = TRUE,
        vec_aes = "distance",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "density_diff",
        fill_label = paste("Biomass\n change (kg/ha)\n", 
            start_time, "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        raster_limits = c(raster_min, raster_max),
        # varidis_option = 
        #white_zero = FALSE,
        white_zero = TRUE,
        mid_fill = "black",
        high_fill = "#66C2A5", #"Steel Blue 4", "#3288BD", #
        low_fill = "#5E4FA2FF", #"Red",
        # high_fill = "#21908CFF", # "#E6F598" "#ABDDA4" "#66C2A5" "#3288BD" "#5E4FA2"
        # low_fill = "#FDE725FF", #"#FEE08B", # "#9E0142" "#D53E4F" "#F46D43" "#FDAE61" "#FEE08B"   
        na_colour = "#66C2A5", #"3288BD", #"Steel Blue 4",
        vec_col = "white",
        vec_alpha = 0.35,
        axis_lables = FALSE,
        transform_col =  fourth_root_power #sqrt # no_trans ##
      ) + ggtitle(paste0(threshold, " units of ", climate, " change below ", 
        biomass_threshold, "% of peak predicted ", species, " biomass" )) #+ theme_black()

@@

    vocc_plot <- plot_vocc(biomass,
      theme_black = TRUE,
       coast = TRUE,
        vec_aes = "distance",
        vec_col = "white",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        #max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "start_density",
        fill_label = paste("Biomass\n change (kg/ha)\n", 
            start_time, "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        viridis_option = "C",
        #raster_limits = c(raster_min, raster_max),
        #white_zero = TRUE,
        #high_fill = "#21908CFF", # "#E6F598" "#ABDDA4" "#66C2A5" "#3288BD" "#5E4FA2"
        #low_fill = "#FDE725FF", #"#FEE08B", # "#9E0142" "#D53E4F" "#F46D43" "#FDAE61" "#FEE08B"
        na_colour = "red",
        vec_alpha = 0.35,
        axis_lables = FALSE,
        transform_col = fourth_root_power # no_trans #
      ) + ggtitle(paste0(threshold, " units of ", climate, " change below ", 
        biomass_threshold, "% of peak predicted ", species, " biomass" )) 
       # +
       #  theme_black()
       # 
    vocc_plot
  })
})

@@

       vocc_plot <- plot_vocc(biomass,
         theme_black = TRUE,
         coast = TRUE,
        vec_aes = "distance",
        vec_col = "white",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "start_density",
        fill_label = paste("Biomass\n change (kg/ha)\n", 
            start_time, "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        viridis_option = "C",
        #raster_limits = c(raster_min, raster_max),
        #white_zero = TRUE,
        #high_fill = "#21908CFF", # "#E6F598" "#ABDDA4" "#66C2A5" "#3288BD" "#5E4FA2"
        #low_fill = "#FDE725FF", #"#FEE08B", # "#9E0142" "#D53E4F" "#F46D43" "#FDAE61" "#FEE08B"
        na_colour = "red",
        vec_alpha = 0.35,
        axis_lables = FALSE,
        transform_col = fourth_root_power # no_trans #
      ) + ggtitle(paste0(threshold, " units of ", climate, " change below ", 
        biomass_threshold, "% of peak predicted ", species, " biomass" ))

>>>>

---
title: "`r paste(params$species)` bioclimatic and biotic vectors for `r paste(params$region)` VOCC"
author: "Philina English"
date: "`r Sys.Date()`"
output: html_document 
params: 
    species: "Redbanded Rockfish" 
    region: "both odd year surveys"
    #region: "West Coast Vancouver Island"
    age: "mature"
    biomass_threshold: "50"
    climate: "temperature"
    threshold: 0.25
editor_options: 
  chunk_output_type: inline
---

@@

    if (climate == "temperature") {
      vocc$diff <- vocc$units_per_decade / 10 * delta_t_total
      vocc_plot <- plot_vocc(vocc,  
        # theme = "black",
        coast = TRUE,
        vec_aes = "distance",
        vec_col = "white",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "temp_e",
        fill_label = paste(" Temperature\n change\n", 
          start_time, "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        raster_limits = c(raster_min, raster_max),
        na_colour = "gray",
        # white_zero = TRUE,
        vec_alpha = 0.35,
        axis_lables = FALSE,
        transform_col = no_trans
      ) + ggtitle(climate)
    }

    if (climate == "do") {
      vocc$diff <- vocc$units_per_decade / 10 * delta_t_total
      vocc_plot <- plot_vocc(vocc, 
        # theme = "black",
        vec_aes = "distance",
        vec_col = "white",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "do_est_e",
        fill_label = paste(" DO change\n", start_time, 
          "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        raster_limits = c(raster_min, raster_max),
        na_colour = "gray",
        # white_zero = TRUE,
        # high_fill = "Steel Blue 4",
        # low_fill = "Red 3",
        vec_alpha = 0.35,
        axis_lables = FALSE,
        transform_col = no_trans
      ) + ggtitle(climate)
    }

@@

      vocc_plot_temp <- plot_vocc(vocc, 
        vec_aes = "distance",
        vec_col = "white",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "temp_e",
        fill_label = paste(" Temperature\n change\n", 
          start_time, "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        # raster_limits = c(raster_min_temp, raster_max_temp),
        # white_zero = TRUE,
        vec_alpha = 0.35,
        axis_lables = FALSE,
        transform_col = no_trans
      ) + ggtitle("temperature")

@@

    if (climate == "temperature") {
      vocc$diff <- vocc$units_per_decade / 10 * delta_t_total
      vocc_plot <- plot_vocc(vocc, 
        theme = "black",
        coast = TRUE,
        vec_aes = "distance",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "diff",
        fill_label = paste(" Temperature\n change\n", start_time, "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        #raster_limits = c(raster_min, raster_max),
        na_colour = "#9E0142",
        # mid_fill = NULL, #"#FFFEC9", #cream
        # high_fill = "#D53E4F",#"Steel Blue 4"
        # low_fill = "#5E4FA2",
        white_zero = TRUE,
        vec_col = "white",
        vec_alpha = 0.45,
        axis_lables = FALSE,
        transform_col =  sqrt #fourth_root_power
      ) + ggtitle(climate) #+ ggpubr::theme_transparent()# +  theme_black()
    }

    if (climate == "do") {
      vocc$diff <- vocc$units_per_decade / 10 * delta_t_total
      vocc_plot <- plot_vocc(vocc,  
        theme = "black",
        coast = TRUE,
        vec_aes = "distance",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "diff",
        fill_label = paste(" DO change\n", start_time, "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        #raster_limits = c(raster_min, raster_max),
        na_colour = "gray",
        white_zero = TRUE,
        high_fill = "Steel Blue 4",
        low_fill = "Red 3",
        vec_alpha = 0.65,
        axis_lables = FALSE,
        transform_col = sqrt# no_trans
      ) + ggtitle(climate)
    }

@@

      vocc_plot_temp <- plot_vocc(vocc,  
        theme = "black",
        coast = TRUE,
        vec_aes = "distance",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "temp_diff",
        fill_label = paste(" Temperature\n change\n", start_time, "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        raster_limits = c(raster_min_temp, raster_max_temp),
        white_zero = TRUE,
      vec_alpha = 0.65,
        axis_lables = FALSE,
        transform_col = sqrt #no_trans
      ) + ggtitle("temperature")

@@

      vocc_plot_do <- plot_vocc(vocc,  
        theme = "black",
        coast = TRUE,
        vec_aes = "distance",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "do_diff",
        fill_label = paste(" DO change\n", start_time, "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        raster_limits = c(raster_min_do, raster_max_do),
        white_zero = TRUE,
        high_fill = "Steel Blue 3",
        low_fill = "Red 2",
      vec_alpha = 0.65,
        axis_lables = FALSE,
        transform_col = sqrt #no_trans
      ) + ggtitle("do")

@@

      vocc_plot <- plot_vocc(vectors,
        theme = "black",
        coast = TRUE,
        vec_aes = "distance",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "diff",
        fill_label = paste("Temperature\n change\n", start_time, "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        raster_limits = c(raster_min, raster_max),
        na_colour = "gray",
        white_zero = TRUE,
      vec_alpha = 0.65,
        axis_lables = FALSE,
        transform_col = no_trans
      ) + ggtitle(paste0(threshold, " units of ", climate, " change below ", 
        biomass_threshold, "% of peak predicted ", species, " biomass" ))
    }

@@

      vocc_plot <- plot_vocc(vectors,
        theme = "black",
        coast = TRUE,
        vec_aes = "distance",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "diff",
        fill_label = paste("DO change\n", start_time, "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        raster_limits = c(raster_min, raster_max),
        na_colour = "gray",
        white_zero = TRUE,
        high_fill = "Steel Blue 4",
        low_fill = "Red 3",
        vec_alpha = 0.65,
        axis_lables = FALSE,
        transform_col = no_trans
      ) + ggtitle(paste0(threshold, " units of ", climate, " change below ", 
        biomass_threshold, "% of peak predicted ", species, " biomass" ))
    }

@@

      vocc_plot_temp <- plot_vocc(vectors,
        theme = "black",
        coast = TRUE,
        vec_aes = "distance",
        min_vec_plotted = input_cell_size,
        NA_label = ".",
        fill_col = "temp_diff",
        fill_label = paste(
          "Change from\n",
          start_time, "to", start_time + delta_t_total, ""
        ),
        raster_alpha = 1,
        raster_limits = c(raster_min_temp, raster_max_temp),
        na_colour = "gray",
        white_zero = TRUE,
        vec_alpha = 0.65,
        axis_lables = FALSE,
        transform_col = no_trans
      ) + ggtitle("temperature")

@@

      vocc_plot_do <- plot_vocc(vectors,
        theme = "black",
        coast = TRUE,
        vec_aes = "distance",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "do_diff",
        fill_label = paste(
          "Change from\n",
          start_time, "to", start_time + delta_t_total, ""
        ),
        raster_alpha = 1,
        raster_limits = c(raster_min_do, raster_max_do),
        na_colour = "gray",
        white_zero = TRUE,
        high_fill = "Steel Blue 4",
        low_fill = "Red 3",
        vec_alpha = 0.65,
        axis_lables = FALSE,
        transform_col = no_trans
      ) + ggtitle("do")

@@

    vocc_plot <- plot_vocc(biomass,
        theme = "black",
        coast = TRUE,
        vec_aes = "distance",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "density_diff",
        fill_label = paste("Biomass\n change (kg/ha)\n", 
            start_time, "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        raster_limits = c(raster_min, raster_max),
        # varidis_option = 
        #white_zero = FALSE,
        white_zero = TRUE,
        mid_fill = "black",
        high_fill = "#66C2A5", #"Steel Blue 4", "#3288BD", #
        low_fill = "#5E4FA2FF", #"Red",
        # high_fill = "#21908CFF", # "#E6F598" "#ABDDA4" "#66C2A5" "#3288BD" "#5E4FA2"
        # low_fill = "#FDE725FF", #"#FEE08B", # "#9E0142" "#D53E4F" "#F46D43" "#FDAE61" "#FEE08B"   
        na_colour = "#66C2A5", #"3288BD", #"Steel Blue 4",
        vec_col = "white",
        vec_alpha = 0.35,
        axis_lables = FALSE,
        transform_col =  fourth_root_power #sqrt # no_trans ##
      ) + ggtitle(paste0(threshold, " units of ", climate, " change below ", 
        biomass_threshold, "% of peak predicted ", species, " biomass" )) #+ theme_black()

@@

    vocc_plot <- plot_vocc(biomass,
      theme = "black",
       coast = TRUE,
        vec_aes = "distance",
        vec_col = "white",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        #max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "start_density",
        fill_label = paste("Biomass\n change (kg/ha)\n", 
            start_time, "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        viridis_option = "C",
        #raster_limits = c(raster_min, raster_max),
        #white_zero = TRUE,
        #high_fill = "#21908CFF", # "#E6F598" "#ABDDA4" "#66C2A5" "#3288BD" "#5E4FA2"
        #low_fill = "#FDE725FF", #"#FEE08B", # "#9E0142" "#D53E4F" "#F46D43" "#FDAE61" "#FEE08B"
        na_colour = "red",
        vec_alpha = 0.35,
        axis_lables = FALSE,
        transform_col = fourth_root_power # no_trans #
      ) + ggtitle(paste0(threshold, " units of ", climate, " change below ", 
        biomass_threshold, "% of peak predicted ", species, " biomass" )) 
       # +
       #  theme_black()
       # 
    vocc_plot
  })
})

@@

       vocc_plot <- plot_vocc(biomass,
         theme = "black",
         coast = TRUE,
        vec_aes = "distance",
        vec_col = "white",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "start_density",
        fill_label = paste("Biomass\n change (kg/ha)\n", 
            start_time, "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        viridis_option = "C",
        #raster_limits = c(raster_min, raster_max),
        #white_zero = TRUE,
        #high_fill = "#21908CFF", # "#E6F598" "#ABDDA4" "#66C2A5" "#3288BD" "#5E4FA2"
        #low_fill = "#FDE725FF", #"#FEE08B", # "#9E0142" "#D53E4F" "#F46D43" "#FDAE61" "#FEE08B"
        na_colour = "red",
        vec_alpha = 0.35,
        axis_lables = FALSE,
        transform_col = fourth_root_power # no_trans #
      ) + ggtitle(paste0(threshold, " units of ", climate, " change below ", 
        biomass_threshold, "% of peak predicted ", species, " biomass" ))

### 2020-02-06 analysis/VOCC/old-code/1-biomass-do-models-fixed-both.Rmd
organize old code

Choose model details
```{r}
# priors <- FALSE
 priors <- TRUE
# covariates <- "+muddy+any_rock"
 covariates <- ""
# covariates <- "+trawled+as.factor(ssid)"
# covariates <- "+muddy+mixed+rocky"
# covariates <- "+mixed+rocky"
# covariates <- "+trawled+muddy+rocky+mixed"
# covariates <- "+trawled+mixed+rocky"
# covariates <- "+trawled+mixed"
# covs <- gsub("\\+", "-", covariates)
# covs <- "-both-tv-depth-ssid"
# covs <- "-both-tv-depth"
covs <- "-log-do"
```

>>>>

Choose model details
```{r}
# priors <- FALSE
 priors <- TRUE
# covariates <- "+muddy+any_rock"
 covariates <- "+as.factor(ssid)"
# covariates <- "+trawled+as.factor(ssid)"
# covariates <- "+muddy+mixed+rocky"
# covariates <- "+mixed+rocky"
# covariates <- "+trawled+muddy+rocky+mixed"
# covariates <- "+trawled+mixed+rocky"
# covariates <- "+trawled+mixed"
# covs <- gsub("\\+", "-", covariates)
# covs <- "-both-tv-depth-ssid"
# covs <- "-both-tv-depth"
covs <- "-log-do"
covs <- "-log-do-ssid"
```

### 2020-02-06 analysis/VOCC/old-code/1-biomass-temp-models-fixed-both.Rmd
organize old code

Species
```{r}
species <- params$species
# # Species run so far...
# species <- "Arrowtooth Flounder"
# species <- "Pacific Cod"
# species <- "Sablefish"
# species <- "Silvergray Rockfish"
# species <- "Lingcod"
# species <- "North Pacific Spiny Dogfish" # note: using all data for maturity thresholds
species <- "Quillback Rockfish"
# species <- "Pacific Ocean Perch"
# species <- "Yelloweye Rockfish"
```

>>>>

Species
```{r}
species <- params$species
# # Species run so far...
# species <- "Arrowtooth Flounder"
# species <- "Pacific Cod"
# species <- "Sablefish"
# species <- "Silvergray Rockfish"
# species <- "Lingcod"
# species <- "North Pacific Spiny Dogfish" # note: using all data for maturity thresholds
# species <- "Quillback Rockfish"
# species <- "Pacific Ocean Perch"
# species <- "Yelloweye Rockfish"
```

### 2020-02-06 analysis/VOCC/old-code/dist-vocc.Rmd
organize old code

Run sdmTMB model (if not done previously).
```{r eval=FALSE}
# # choose the spatial range to model
dat <- data %>% dplyr::filter(year > 2003) # %>% select(year, ssid, X, Y, temperature_c, depth_scaled, depth_scaled2)
#nd <- nd_1 # %>% filter(ssid == 4)

>>>>

Run sdmTMB model (if not done previously).
```{r eval=FALSE}
# # choose the spatial range to model
dat <- data #%>% dplyr::filter(year > 2003) # %>% select(year, ssid, X, Y, temperature_c, depth_scaled, depth_scaled2)
#nd <- nd_1 # %>% filter(ssid == 4)
